% ┌───────────────────────────────────────────────────────────────┐
% │ Contents of letter.tex                                        │
% ├───────────────────────────────────────────────────────────────┘
% │
% ├── PREAMBLE
% ├──┐BODY
% │  ├── HEADER
% │  ├── SALUTATION
% │  ├── OPENING
% │  ├── QUALIFICATIONS
% │  ├── CLOSING
% │  └── SIGN-OFF
% │
% └───────────────────────────────────────────────────────────────

% ################################################################ PREAMBLE

\author{Erica Ruggiero}
\title{Erica Ruggiero Cover Letter}

\documentclass[a4paper,11pt,letter]{business}

%\setmainfont{Minion 3}

% ################################################################ BODY

\begin{document}

% ################################ HEADER

\avatar{photo}
\name{Erica Ruggiero}
\city{Cambridge, MA 01242}
\mobile{(413) 464-4238}
\mail{Erica.Ruggiero@sloan.mit.edu}
\website{https://linkedin.com/in/erikaruggiero}

\thispagestyle{text}

% ################################ SALUTATION

\vspace{\dimexpr 10mm-\baselineskip\relax}

Mr. Tim Apple\\
University Relations\\
Apple\\
1 Infinite Loop\\
Cupertino, CA 95014

Dear Mr. Apple,

% ################################ OPENING

I am excited to be applying for a Product Marketing Internship position with Apple.
I had the pleasure of attending the Apple information session at Sloan and was struck by the passion and drive exhibited by all the presenters.
Product Marketing in particular stood out to me because it blends core business principles with a passion for technology and the product.
I believe my technical, communication, and teamwork skills would make me a valuable addition to Apple.

% ################################ QUALIFICATIONS

As a design engineer at Intel, I worked on products for our server and data center businesses.
I was constantly engaged on projects with extensive deliverables and short deadlines.
One such project was leading the development of a test chip commissioned by Intel researchers.
The test chip had a set of broad specifications that I had to translate first into specific design goals and then into physical circuitry.
Once I had a design in place, I coordinated with internal stakeholders to iterate on the design as the experiment for the chip evolved.
I set up a series of milestones to ensure that my schedule would be met, and assembled a team of engineers to assist me in the project.
I concurrently owned several technical aspects of the project, while also managing the overall project and keeping close communications with the internal customers who would ultimately be using the chip.
Despite some significant setbacks late in the project, we managed to deliver the chip ahead of schedule.

Towards the end of my time at Intel, I assumed ownership over a large code database which was used by engineers from three different functional roles and across three different Intel projects, all of whom were invested in different aspects of the database.
Part of this role was convincing each project team to use the central database, rather than branching off and creating their own version.
I achieved this by first modifying the code generation process to be more modular and adaptable to different project specifications.
I then demonstrated to each team the benefits in terms of engineering hours and scalability that the central database afforded them.
Once I had teams on board, I engaged in significant cross-team communication, prioritizing code change requests from different internal customers and presenting to wide audiences, including project leadership, about the use-model and content of the database.

% ################################ CLOSING

With my strong technical and analytical background, as well as the teamwork, communication and business skills I am developing at Sloan, I know that I can bring a strong, unique perspective to the Apple Product Marketing team.
Thank you for your consideration for this position and I look forward to discussing my experience further in a personal interview.

% ################################ SIGN-OFF

Sincerely,

%\adjustimage{width=40mm}{signature}

Erica Ruggiero

\end{document}

